DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-06 paper/comparison.tex
integrate related work with background section
revise conclusion
..

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/compare_benchmark}
  \caption{Inferencing time across platforms based on number of cores 
used.}
  \label{fig:sys_bench}
\end{figure}

@@

Another intersting observation is that TX2 (GPU) also suffers
considerable execution time increase (2.5X) despite the fact that the
co-scheduled synthetic tasks do not utilize the GPU. In other words,
the DNN model has dedicated access to the GPU. This is, however, a
known characteristic of integrated CPU-GPU architectue based
platforms that both CPU and GPU share the same memory
subsystem~\cite{Ali2017}.

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/compare_benchmark}
  \caption{Average control loop execution time in the presence of an
    increasing number of memory intensive applications on idle CPU cores.}
  \label{fig:sys_bench}
\end{figure}

@@

Another intersting observation is that TX2 (GPU) also suffers
considerable execution time increase (2.5X) despite the fact that the
co-scheduled synthetic tasks do not utilize the GPU. In other words,
the DNN model has dedicated access to the GPU. This is, however, a
known characteristic of integrated CPU-GPU architectue based
platforms that both CPU and GPU share the same memory
subsystem~\cite{Ali2017}. As a result, TX2 (GPU) fails to meet the
10ms deadline for 100 Hz control that would have been feasible if
there is no contention between the CPU cores and the GPU.

### 2017-10-06 paper/main.tex
..

\maketitle
\thispagestyle{empty}
\begin{abstract}
We present DeepPicar, a low-cost deep neural network (DNN) based
autonomous car platform. DeepPicar is a small scale
replication of a real self-driving car called Dave-2 by NVIDIA, which
drove public roads using a deep convolutional network (CNN) that
takes images from a front-facing camera as input and produces
car steering angles as output. DeepPicar uses the exact same network
architecture---9 layers, 27 million connections and 24K
parameters---and can be trained to drives itself in real-time using a
web camera and a modest Raspberry Pi 3 quad-core platform.
Using DeepPicar, we analyze Pi 3's computing capabilities to 
support end-to-end deep learning based real-time control of autonomous
vehicles. We also systematically compare other contemporary embedded
computing platforms using the DeepPicar's CNN based real-time control
software as a workload. 
We find all tested platforms, including the Pi3, are capable of
supporting deep-learning based real-time control, from 20 Hz up to 100
Hz, depending on hardware platform. 
However, shared resource contention remains an
important issue that must be considered in applying deep-learning
models on shared memory based embedded computing platforms.

>>>>

\maketitle
\thispagestyle{empty}
\begin{abstract}
We present DeepPicar, a low-cost deep neural network (DNN) based
autonomous car platform. DeepPicar is a small scale
replication of a real self-driving car called Dave-2 by NVIDIA, which
drove public roads using a deep convolutional network (CNN) that
takes images from a front-facing camera as input and produces
car steering angles as output. DeepPicar uses the exact same network
architecture---9 layers, 27 million connections and 24K
parameters---and can be trained to drives itself, in real-time, using a
web camera and a modest Raspberry Pi 3 quad-core platform.
Using DeepPicar, we analyze Pi 3's computing capabilities to 
support end-to-end deep learning based real-time control of autonomous
vehicles. We also systematically compare other contemporary embedded
computing platforms using the DeepPicar's CNN based real-time control
software as a workload. 
We find all tested platforms, including the Pi3, are capable of
supporting deep-learning based real-time control, from 20 Hz up to 100
Hz, depending on hardware platform. 
However, shared resource contention remains an
important issue that must be considered in applying deep-learning
models on shared memory based embedded computing platforms.
